The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-06-20 manuscript.Rmd
edit manuscript

We also need to better coordination in describing new species; so that efforts are not duplicated.

Possibly also need to set guidelines on how to treat cases where the molecular data alone is too ambiguous.

@@

Regional faunistic lists assembled and curated by taxonomic experts typically provide a comprehensive and detailed account of species that are known to occur in a given geographic area. We assessed how faunistic lists assembled over decades by specialists compare with records in public databases for the same geographic area. We parsed faunistic lists to extract marine invertebrates from the Gulf of Mexico [@Tunnell2009] and from the Pacific Northwest [@Kozloff1987]. Our goals were (1) to compare  the species lists for these geographic areas assembled by experts with the records found in databases; (2) to assess the proportion of species included in the expert lists that have records in public databases.

>>>>

@@

Regional faunistic lists assembled and curated by taxonomic experts provide a comprehensive and detailed account of species that are known to occur in a given geographic area. We assessed how faunistic lists assembled over decades by specialists compare with records in public databases for the same geographic area. We parsed faunistic lists to extract marine invertebrates from the Gulf of Mexico [@Tunnell2009] and from the Pacific Northwest [@Kozloff1987]. Our goals were (1) to compare  the species lists for these geographic areas assembled by experts with the records found in databases; (2) to assess the proportion of species included in the expert lists that have records in public databases.
